Governing through patronage: the bargain for education in decentralized Brazil

### 2020-09-11 paper/paper.tex
continue editing patronage_education paper

In Brazil, responsibility for primary education is delegated to local governments \citet{paschoal_historia_2009}. The municipal educational system has increased in relevance over the past few decades, as municipalities took on a larger proportion of students from state-level governments. Figure \ref{fig:enroll} plots the total number of students in primary education per government level, including private schools. As of 2016, over 25 million students were enrolled in over 115 thousand municipal schools.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/descriptive_enrollment.pdf}
    \caption{enrollment}
    \label{fig:enroll}
\end{figure}

@@

>>>>

In Brazil, the responsibility to provide public, primary education is primarily delegated to local governments \citet{paschoal_historia_2009}. In this critical learning period, students acquire skills such as reading/writing, as well as foundational concepts in math such as addition and substraction. The municipal educational system has increased in relevance over the past few decades, and currently over 60 percent of lower school strudents attend a public school. Figure \ref{fig:enroll} plots the total number of students in primary education per government level, including private schools. As of 2016, over 25 million students were enrolled in over 115 thousand municipal schools.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.6\linewidth]{plots/descriptive_enrollment.pdf}
    \caption{\textbf{Student enrollment by administration.}}
    \label{fig:enroll}
\end{figure}

@@

\blue{Insert more information and descriptive paragraph on turnover index here}
